\documentclass[helvetica,narrow,english,booktabs,a4paper]{moderncv}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[scale=0.75]{geometry}
\geometry{tmargin=2cm,bmargin=3cm}
\usepackage{microtype}
\usepackage{mdwlist}

\renewcommand{\ttdefault}{phv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}

\name{Dario}{Bertini}
\phone[mobile]{+44 7960454417}
\email{berdario@gmail.com}
\social[github]{berdario}

\AfterPreamble{\hypersetup{colorlinks=true, urlcolor=blue}}

\begin{document}
  \makecvtitle

  \section{Work experience}
  References available upon request.
  \\
  \\
  \cventry{August 2015 - ...}{Software Engineer}{Toptal}{}{}{}
  \leavevmode\\
  \\
  \cventry{November 2014 - July 2015}{Security Consultant}{NCCGroup}{}{}{}
  Working at NCCGroup bolstered my knowledge of network protocols, web apps security, Linux systems and Windows domains security thanks to the extensive internal training. After the training I developed some tools for internal use and I was tasked with performing security assessments for multinational companies. Such assessments covered a range of technologies (.NET, Python, PHP, etc.) and had elements of both white box code reviews and black box tests. XSS, CSRF, clear-text storage of passwords, path traversal and remote code execution are among the kind of vulnerability that I found and documented.
  \\
  \\
  \cventry{September 2014 - October 2014}{Software developer}{CommentBubble}{}{}{}
  Setup the project into a proper Python module, as a building block for testing and continuous integration. Discovered an Insecure Direct Object Reference vulnerability and wrote tests to prevent its regression.
  \\
  \\
  \cventry{February 2014 - October 2014}{Software developer/devops}{Audiencerate}{}{}{}
  Managed the provisioning of the system, which has a load of about 100 req/s. Wrote some simple integration/acceptance tests, added monitoring into the system, rewrote the code dealing with the database and tested all the software before each production deployment. (Technologies used: Ansible, Vagrant, Selenium, Clojure, Python.)

  \section{Personal skills and competences}
  \subsection{Programming Languages}

\cvlistitem{Python: Advanced knowledge. Used for web development, dealing with binary formats, scripting as well as cpu-intensive loads, wrapping native libraries with ctypes, sketching out some proof of concept gui. I also read the internal details of some Python implementations and wrote my own \href{https://github.com/berdario/pew}{simple tool to manage virtual environments}.}
\cvlistitem{Clojure: Used on and off since 2013, I'm comfortable with the language and the surrounding tooling.}
\cvlistitem{Haskell: Good knowledge.}
\cvlistitem{Java: Good knowledge and experience with legacy Java codebases.}
\cvlistitem{Ruby: Contributed some simple patches upstream (e.g. \url{http://git.io/W7e-9w} \url{http://git.io/7kM4Gw}).}
\cvlistitem{Working knowledge of F\#, Ocaml, Javascript, Scala, C, Vala, C\#, SQL.}

  \clearpage
  \subsection{Software Tools and Libraries}
  DVCS (Bazaar, Mercurial, Git, Darcs), Continuous Integration, Package/Dependencies Manager/Build Systems, Bug
  Trackers, I18n and L10n toolchain, IDEs/Editors, DB/Data Stores
  (Postgresql, Mongodb, Redis), OpenGL, MapReduce, Documentation (Sphinx, Markdown),
  Configuration Management and Deployment (Ansible), Emscripten, Powershell, Lucene, JNI, Jython.
  \subsection{Other Computer competences}
  Experienced with Linux (and with Windows and MacOSX to a lesser extent), contributed/maintained some packages for the Nixos Linux distribution.\\
  For further details I have some repositories online at: \url{https://github.com/berdario}.

  \section{Education and training}
  Bachelor Degree in Computer Engineering\\
  \cvitem{Subjects covered}{Network security, Languages and compilers, Information theory, C++ and Java programming courses, Databases, Operating systems, Theoretical computer science,  Project Management, Artificial Intelligence, Information Retrieval, Stochastic Models.\\
Thesis Work: Adaptation of a georeferentiation search application for a client-server architecture}
  \cvitem[15pt]{Institution}{Università degli Studi di Bergamo}

  Erasmus study period in Computer Science at University of Southern Denmark\\
  \cvitem{Subjects covered}{String Algorithms, Programming Languages, Cloud Computing, Advanced Data Structures, Online Algorithms, Combinatorial Optimization.}

  \section{Languages}
  \cvitem{Italian}{Native language}
  \cvitem{English}{Full professional proficiency}

  \section{Social skills and competences}
  I regularly attend IT meetups, was an active member of the Bergamo Linux User Group (\url{http://bglug.it}) and helped start another small programming tech group: Codelovers (\url{http://codelovers.it}).

\end{document}
